Bioverse: Origins of Life

### 2024-06-11 src/tex/ms.tex
include NUV distribution plot

>>>>

\subsubsection{selectivity of a generic transit survey}
In Section~\ref{sec:results-semianalytical}, we demonstrated that the probability of obtaining true strong evidence for the hypothesis that life only originates on planets with a minimum past \gls{NUV} flux is sensitive to the distribution of sampled past \gls{NUV} fluxes, i.e., the selectivity of the survey (compare Figure~\ref{fig:semian_selectivity}).
The maximum \gls{NUV} distribution of our generic transit survey is rather unimodal with a median around \SI{500}{\erg\per\second\per\centi\meter\squared} (see Figure~\ref{fig:nuv_distribution}), leading to a selectivity of roughly \var{selectivity_transit_volume-lim}.
\begin{figure}
    \script{nuv_distribution.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/nuv_distribution}
        \caption{Distribution of maximum past \gls{NUV} flux in a generic volume- and magnitude-limited transit survey. The best-fit beta distribution (gray) corresponds to a selectivity of \var{selectivity_transit_volume-lim}.}
        \label{fig:nuv_distribution}
    \end{centering}
\end{figure}
